R Notebook

### 2016-10-05 manuscript/draft.Rmd

* Mixed model for observer effort \& site effects
* Naive AR1 model (adjusted for observer effects)
* species-level GBM w/ mixed model point estimates as bonus predictors where available
* richness-level GBM w/ mixed model point estimates as bonus predictors where available
* JSDM

@@

* Temporal richness variability doesn't track the predictors we use; sites have "inertia"
* More important to use a reasonable error model than to get the best predictors \& basis expansions
* We've posted predictions for the next N years of BBS data, using several methods, and invite others to do so as well.
* In many ways, this is the best-case scenario for SDMs:
  * large data set, known \& consistent sampling technique over a period of decades
  * True absences
  * extended predictor set
  * birds arguably migrate quickly enough to make equlibrium \& especially space-for-time assumptions less ridiculous
  * errors for individual species can cancel out; only asking for aggregate values
* None of the models actually work all that well, compared to baseline.
* Value of stacking versus predicting the quantitity of interest directly
* Maybe richness is too coarse
  * abundance
  * species-level

>>>>

* Mixed model for observer effort \& site effects
* Naive AR1 model (adjusted for observer effects)
* species-level GBM w/ mixed model point estimates as bonus predictors where available
* richness-level GBM w/ mixed model point estimates as bonus predictors where available
* JSDM
* Ensembles (weighted and unweighted)

@@

* None of the models actually work all that well, compared to baseline.
* Temporal richness variability doesn't track the predictors we use; sites have "inertia"
  * Cite 3 papers Ethan found on consistancy of alpha even when composition changes dramatically
  * Good for absolute accuracy, little room for improvement over baseline
  * Maybe richness is too coarse
    * abundance
    * species-level
* More important to use a reasonable error model than to get the best predictors \& basis expansions
* Ensembles help/don't help (depending on results)
* Point estimate error versus coverage
* In many ways, this is the best-case scenario for SDMs:
  * large data set, known \& consistent sampling technique over a period of decades
  * "True" absences
  * extended predictor set
  * birds arguably migrate quickly enough to make equlibrium \& especially space-for-time assumptions less ridiculous
  * errors for individual species can cancel out; only asking for aggregate values
* Value of stacking versus predicting the quantitity of interest directly
* Need to start doing this, even if we're bad at it.
  * We've posted predictions for the next N years of BBS data, using several methods, and invite others to do so as well.
